### 2018-10-21 Sections/state_of_the_art.tex
Bib errors fixed

	Quantum teleportation over fibre networks in Hefei and Calgary were demonstrated, with lengths of dozens of kilometres. & \cite{bib:Nat_Phot_10_671, bib:Nat_Phot_10_676} \\

@@

	Using 5-photon entanglement, open-destination teleportation was implemented, whereby an unknown quantum state was teleported onto a superposition of 4 destination photons, which could be read out at any location -- a type of `broadcasting'. & \cite{bib:Nat_430_54} \\

@@

In 2015, \cite{bib:Nat_526_682} for the first time achieved entanglement swapping using independent entangled photon sources separated by 1.3km in a real-world environment. However, the wavelength of the photons used in this experiment was 637nm (transmission loss \mbox{$\sim 15$dB/km}), which is not conducive to achieving long-distance entanglement swapping since it is far greater than the transmission loss of communication-band photons in fibre (\mbox{$\sim 0.2$dB/km}). Based on the techniques in \cite{bib:Nat_phot_10_671, bib:Nat_phot_10_676}, longer-distance entanglement swapping may be possible in the near future.

@@

Starting with two entangled atom-photon pairs, we can project the two atomic qubits into a maximally entangled state by performing a Bell state measurement on the two photons \cite{bib:Nature_428_153, bib:PRL_96_030404}. In 2007, \cite{bib:Nature_449_68} entangled two trapped atomic ions separated 1m apart using entanglement swapping, exploiting interference between photons emitted by the ions. The fidelity of the states of the entangled ions was $0.63(3)$. In subsequent experiments \cite{bib:PRL_100_150404}, the ion-ion entanglement fidelity was improved to $0.81$. Similarly, \cite{bib:Nature_454_1098} entangled two atomic ensembles, each originally with a single emitted photon, by performing a joint Bell state measurement on the two single photons after they had passed through a 300m fibre-based communication channel. In 2015, \cite{bib:hensen2015loophole} generated robust entanglement (estimated state fidelity of $0.92\pm0.03$) between the two distant spins by entanglement swapping in the scheme of \cite{bib:BarrettKok05, bib:Nature_497_86}. Such a high fidelity is sufficient to successfully perform loophole-free Bell inequality tests.

>>>>

	Quantum teleportation over fibre networks in Hefei and Calgary were demonstrated, with lengths of dozens of kilometres. & \cite{bib:sun2016quantum, bib:Nat_Phot_10_676} \\

@@

	Using 5-photon entanglement, open-destination teleportation was implemented, whereby an unknown quantum state was teleported onto a superposition of 4 destination photons, which could be read out at any location -- a type of `broadcasting'. & \cite{bib:zhao2004experimental} \\

@@

In 2015, \cite{bib:Nat_526_682} for the first time achieved entanglement swapping using independent entangled photon sources separated by 1.3km in a real-world environment. However, the wavelength of the photons used in this experiment was 637nm (transmission loss \mbox{$\sim 15$dB/km}), which is not conducive to achieving long-distance entanglement swapping since it is far greater than the transmission loss of communication-band photons in fibre (\mbox{$\sim 0.2$dB/km}). Based on the techniques in \cite{bib:sun2016quantum, bib:Nat_phot_10_676}, longer-distance entanglement swapping may be possible in the near future.

@@

Starting with two entangled atom-photon pairs, we can project the two atomic qubits into a maximally entangled state by performing a Bell state measurement on the two photons \cite{bib:blinov2004observation, bib:PRL_96_030404}. In 2007, \cite{bib:Nature_449_68} entangled two trapped atomic ions separated 1m apart using entanglement swapping, exploiting interference between photons emitted by the ions. The fidelity of the states of the entangled ions was $0.63(3)$. In subsequent experiments \cite{bib:PRL_100_150404}, the ion-ion entanglement fidelity was improved to $0.81$. Similarly, \cite{bib:Nature_454_1098} entangled two atomic ensembles, each originally with a single emitted photon, by performing a joint Bell state measurement on the two single photons after they had passed through a 300m fibre-based communication channel. In 2015, \cite{bib:hensen2015loophole} generated robust entanglement (estimated state fidelity of $0.92\pm0.03$) between the two distant spins by entanglement swapping in the scheme of \cite{bib:BarrettKok05, bib:bernien2013heralded}. Such a high fidelity is sufficient to successfully perform loophole-free Bell inequality tests.
